---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# hackr

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/tyluRp/hackr.svg?branch=master)](https://travis-ci.org/tyluRp/hackr)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/tyluRp/hackr?branch=master&svg=true)](https://ci.appveyor.com/project/tyluRp/hackr)
[![Codecov test coverage](https://codecov.io/gh/tyluRp/hackr/branch/master/graph/badge.svg)](https://codecov.io/gh/tyluRp/hackr?branch=master)
<!-- badges: end -->

The goal of hackr is to wrap the Hacker News API in R.

## Installation

You can install the development version from GitHub with:

``` r
# install.packages("devtools")
devtools::install_github("tylurp/hackr")
```

## Example

You can fetch top stories, new stories, or best stories. By default, a `tibble` is returned, if there is a _kids_ column (comments identifier), it will be nested in order to return a single row for each story. You can override this with `unnest = TRUE` and show comments with `comments = TRUE`:

```{r example, message=FALSE}
library(hackr)
library(dplyr)

hackr_top_stories()
hackr_top_stories(n = 1, unnest = TRUE, comments = TRUE) %>% 
  select(title, comment)
hackr_new_stories(2)
hackr_best_stories(2)
```

That's it for now. Will add more features soon.
